Fixing Vulnerabilities Potentially Hinders Maintainability

### 2020-05-28 paper/icsme20.tex
abstract hot fixes

\begin{abstract}
Security is a requirement of utmost importance to produce software with 
high quality. However, there is still a considerable amount of 
vulnerabilities being discovered and fixed, almost weekly. We suspect 
that when developers address these vulnerabilities on their codebases, 
they actually affect the maintainability of software, potentially 
introducing other vulnerabilities. This paper evaluates the impact of 
patches to improve security on the maintainability of open-source software. 
Maintainability is measured based on the Better Code Hub’s model of 10 
guidelines using a dataset including 1335 security commits.
Results show evidence of a new trade-off between security and maintainability, i.e., 
when developers may be hindering the software maintainability or even introducing 
new vulnerabilities while patching vulnerabiliteis.
We conclude that changes to codebases while patching 
vulnerabilities need to be performed with extra care (e.g., using tools
for patch risk assessment), computer science
curricula needs to be updated and more secure programming languages are necessary.
\end{abstract}
\begin{IEEEkeywords}
Security, Software Maintenance, Open-Source Software
\end{IEEEkeywords}

>>>>

\begin{abstract}
Security is a requirement of utmost importance to produce software with 
high quality. However, there is still a considerable amount of 
vulnerabilities being discovered and fixed, almost weekly. We suspect 
that when developers address these vulnerabilities on their codebases, 
they actually affect the maintainability of software. This paper evaluates the 
impact of patches to improve security on the maintainability of open-source 
software. 
Maintainability is measured based on the Better Code Hub’s model of 10 
guidelines using a dataset including 1335 security-related commits.
Results show evidence of a trade-off between security and maintainability, i.e., 
developers may be hindering the software maintainability or even introducing 
new vulnerabilities while patching vulnerabiliteis.
The implications of our study are that changes to codebases while patching 
vulnerabilities need to be performed with extra care (e.g., using tools
for patch risk assessment), computer science
curricula needs to be updated and more secure programming languages are necessary.
\end{abstract}
\begin{IEEEkeywords}
Security, Software Maintenance, Open-Source Software
\end{IEEEkeywords}
